Thermodynamic response functions in a cell fluid model

### 2024-09-12 dobush_et_al_ujp_UTF8.tex
adjusted figures according to ujp styleguide
remove acknowledgement from main tex file
add ukr abstract

	\begin{abstract}
		Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential. These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble. The calculated quantities are presented graphically as functions of density and chemical potential.
	\end{abstract}

@@

	\vskip3mm \textit{Acknowledgement.}

@@

	\vspace*{-5mm}\rezume{%Резюме укр. мовою
		О.А.~Добуш, М.П.~Козловський, Р.В.~Романік, І.В.~Пилюк}{ТЕРМОДИНАМІЧНІ ФУНКЦІЇ ВІДГУКУ КОМІРКОВОЇ МОДЕЛІ} {Текст резюме укр. мовою.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
			с\,л\,о\,в\,а:} коміркова модель, потенціал Морзе, термодинамічні функції відгуку.}

>>>>

	\begin{abstract}
		Thermodynamic response functions, namely the isothermal compressibility, the thermal pressure coefficient, and the thermal expansion coefficient, are calculated for a many-particle system interacting through a modified Morse potential. These calculations are based on an equation of state previously derived for a cell fluid model in the grand canonical ensemble. The calculated quantities are presented graphically as functions of density and the effective chemical potential.
	\end{abstract}

@@

@@

	\vspace*{-5mm}\rezume{%Резюме укр. мовою
		О.А.~Добуш, М.П.~Козловський, Р.В.~Романік, І.В.~Пилюк}{ТЕРМОДИНАМІЧНІ ФУНКЦІЇ ВІДГУКУ КОМІРКОВОЇ МОДЕЛІ} {В роботі преведено розрахунки термодинамічних функцій відгуку - ізотермічної стисливості, термічного коефіцієнта тиску, та термічного коефіцієнта розширення - для системи частинок, які взаємодіють через модифікований потенціал Морзе. Ці розрахунки проводились виходячи з рівняння стану отриманого в попередній роботі для коміркової моделі плину в формалізмі великого канонічного ансамблю. Залежності отриманих величин від густини і ефективного хімічного потенціалу представлені графічно.}{\textit{К\,л\,ю\,ч\,о\,в\,і\,
			с\,л\,о\,в\,а:} коміркова модель, потенціал Морзе, термодинамічні функції відгуку.}
